Physcraper: A Python package for continually updated phylogenetic trees using the Open Tree of Life

### 2021-03-30 sources/bmc_template_submission/bmc_article.tex
pylint implementation
pylint scores

>>>>

Physcraper is implemented with Python and can also be run on the command line.
It currently consists of 12 modules.
%% , classes, methods and functions.%%
For testing and improving the quality of the Python code syntax in the Phsycraper code,
we used the Pylint \cite{pylintWeb, pylintManual} software with a configuration file.
We improved the code syntax on modules with low Pylint scores and fixed errors by
following Pylint's recommendations.
In some cases, we overruled Pylint's recommendations by using its check-disabling
system. As of now, all modules have a Pylint score of 10/10.
